EldersAIR: manuscript tables/figures

### 2021-05-26 main_analysis_pm.Rmd
new ambient temp data

@@

plot(itt_pm_results_primary, main = "ITT Primary Model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_pm_results_primary), main = "ITT Primary Model")
qqline(residuals(itt_pm_results_primary))

#table(analysis_data$wood_collect_method, analysis_data$area, analysis_data$winter_id)
#table(analysis_data$wood_collect_3level, analysis_data$area, analysis_data$winter_id)
```

@@

obs <- pm_data_2row %>% 
  filter(!is.na(outcome)) %>% 
  filter(!is.na(baseline_outcome)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(wood_collect_method)) %>%
  group_by(area, treatment) %>% 
  count()
obs
save_contrasts
Anova(itt_results_int)

>>>>

```{r}
table_data <- analysis_data %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  distinct(area, home, winter_id, .keep_all = T)

table(table_data$wood_collect_method, table_data$area, table_data$winter_id)

table(table_data$wood_collect_3level, table_data$area, table_data$winter_id)

table(table_data$stove_grade, table_data$area, table_data$winter_id)

table(table_data$residents_smoke, table_data$area, table_data$winter_id)

table(table_data$burn_level_3level, table_data$area, table_data$winter_id)

table(table_data$stove_age_2level, table_data$area, table_data$winter_id)

summary_data <- analysis_data %>% 
  group_by(area, winter_id, wood_collect_3level) %>% 
  summarize(mean(moisture_ave, na.rm = T),
            median(moisture_ave, na.rm = T))
summary_data
```

@@

@@

obs <- pm_data_2row %>% 
  filter(!is.na(outcome)) %>% 
  filter(!is.na(baseline_outcome)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(wood_collect_3level)) %>%
  group_by(wood_collect_3level, treatment) %>% 
  count()
obs
save_contrasts
Anova(itt_results_int)

### 2021-05-26 manuscript_tables_figures.Rmd
new ambient temp data

---
title: 'EldersAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 1 March 2021, Updated 19 April 2021"
output:
  powerpoint_presentation: default
---

@@

# Number of exposure samples in Figure 1
```{r}
# Step 1: Winter 1 samples
exposure_check <- elders_pm %>% 
  arrange(area, home, winter_id, sampling_visit) %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  filter(winter_id == 1) %>% 
  count(area)

@@

# Step 2: Winter 2 samples
exposure_check <- elders_pm %>% 
  filter(!is.na(treatment)) %>% 
  arrange(area, home, winter_id, sampling_visit) %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  filter(winter_id == 2) %>% 
  count(treatment, area)

@@

>>>>

---
title: 'EldersAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 1 March 2021, Updated 24 May 2021"
output:
  powerpoint_presentation: default
---

@@

# Number of exposure samples in Figure 1
```{r} 
# Step 1: Winter 1 samples
exposure_check <- elders_cleaned_dataset_by_visit %>% 
  arrange(area, home, winter_id, sampling_visit) %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  filter(!is.na(mp_mean_visit)) %>% # mp_mean_visit or pm_mean_visit
  filter(winter_id == 1) %>% 
  count(area)

@@

# Step 2: Winter 2 samples
exposure_check <- elders_cleaned_dataset_by_visit %>% 
  filter(!is.na(treatment)) %>% 
  arrange(area, home, winter_id, sampling_visit) %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  filter(!is.na(mp_mean_visit)) %>% # mp_mean_visit or pm_mean_visit
  filter(winter_id == 2) %>% 
  count(treatment, area)

@@

```{r}
pm_cutoff_table <- elders_cleaned_dataset_by_visit %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  distinct(area, home, winter_id, .keep_all = T) %>% 
  mutate(epa_12 = if_else(pm_mean_winter > 12, "Above", "Below"),
         epa_35 = if_else(pm_mean_winter > 35, "Above", "Below")) %>% 
  group_by(winter_id, treatment, epa_35) %>% 
  count()
pm_cutoff_table
```
